I would have to say that I have learned quite a lot working on this project.
I've worked on many solo projects but I've worked on very few group projects, even at my internship.
Working in a group is a very different experience from working alone and I think that is the highlight of this course.

On the technical level, I learned how to use a ton of different technologies throughout the term.
I was familiar with web development but using Django was a new take on web development that I enjoyed learning.
In addition to this my knowledge of Python has increased through much use of it during this project.
This project has also given me experience in picking up new technologies and libraries and learning how to use them quickly which is a very valuable skill to have.

Working with a client to deliver something that they want was an excellent experience and something I found very rewarding.
Learning how to listen to what they want and work with them to find a reasonable solution is an important process that I feel I've learned a good deal about.
Working in a group has also been a valuable experience.
We've learned how to use a mix of working independently and working together in order to accomplish goals and meet deadlines.
I've definitely learned that at times I need to yield to my teammates judgment and trust them to make the correct decisions.

Overall I'm happy with what I've gained from working on this project.
If I were to do it all over from the start, I can't think of too many things that I would want to change.
I think it would have been very useful if we had gotten our ideas nailed down sooner with our client.
It also would have been cool if we had better defined stretch goals as we ran out of things to work on at the start of spring term.
Even with these caveats, I would say that this was a very successful project.