% Who requested it?
% Why was it requested?
% What is its importance?
% Who was/were your client(s)?
% Who are the members of your team?
% What were their roles?
% What was the role of the client(s)? (I.e., did they supervise only, or did they participate in doing development)
Professor Dave Lytle, head of the Lytle Lab in the Department of Integrative Biology at Oregon State University, requested this project.
His research team had collected five years of insect samples from Department of Defense bases and amalgamated the observations into a large, somewhat messy database.
He asked our team for a visualization system to help make sense of the data.
Such a system would aid researchers in data analysis, and help the Department of Defense to make informed land management decisions.
Dr. Lytle and his research team sponsored the project and acted as clients for the product.
We met with them periodically throughout each term to go over progress and goals.
They were, of course, involved in design decisions, but left the implementation details primarily to us.

Our team consists of Jasper LaFortune, Alec Shields, and Ty Skelton.
We each had a distinct role in development and team leadership.
Jasper 	developed the Filter View 	and led the team's presentations, 			including organizing the poster, video reports, and elevator pitch.
Alec 	developed the Map View 		and led the team's external communications, including contacting our clients and submitting assignments.
Ty 		developed the Graph View 	and led the team's internal communications, including organizing meetings and individual tasks.
Development and leadership responsibilities were shared fairly among all three members.
