% What did you learn from all this? One per team member.
%   What technical information did you learn?
%   What non-technical information did you learn?
%   What have you learned about project work?
%   What have you learned about project management?
%   What have you learned about working in teams?
%   If you could do it all over, what would you do differently?
% Be honest here -- no B.S.

I am a firm believer in the educational benefits of long-term projects.
When I am a teacher, I will be the asshole teacher who assigns lots of projects.
My students will hate me.
But at the end of the year, they will be able to look back at all of the skills they could not have learned any other way.
I know from experience with my thesis and this project.

In the course of this project, I learned technical information on the fly.
When I needed to know how to use Django, I read up and the documentation and figured it out.
When I needed to know how to use Javascript libraries, I looked up examples and figured it out.
Besides now having these skills, I have honed my ability to pick up new technical skills.
I have also acquired an appreciation for the patience of a long-term project.
This project was a marathon, not a sprint.
It seems daunting at first, but from the other side, it is a lot more relaxed than a sprint.
Having many small deadlines along the way keeps things from building up, and you do not find yourself so out of breath at the end.

Of course, I did not do this on my own.
When I needed help, I had it from my teammates, who were excellent.
If this project taught me one thing, it is the importance of a good team.
I have rarely been so pleased with a group for group work.
I will definitely be making future career decisions based on how well I could work with my prospective colleagues.
The most important thing we did to foster good teamwork was to stay in contact.
Thanks to weekly meetings, it was hard to ever get more than a week behind.

My only regret is that this project became more implementation than research.
Our primary objective was to make a product that our client was happy with, which we did.
But we did not necessarily contribute generalizable knowledge to the field of visualization.
I think this comes of having a sponsor whose area of research was outside of Computer Science.
As a result, our solution contributed more to biology than Computer Science.
In other words, being a bit of an academic, I am a bit disappointed that my work is actually of practical use.
