Learning to use new tech is always a challenge when taking on a new project but we had a lot of good resources on our side.
Almost all of the things we needed to learn we found out on our own online.

Probably the most helpful resource we found in learning Django, Python, and all of the other libraries we used was StackOverflow.
When we were setting up Django there were a lot of questions we had that could be found in documentation but perhaps weren't easy to find.
This is what StackOverflow was so useful for, finding answers to these common questions.
Learning to use Django definitely came with some pain and Stack definitely is a huge help for solving bugs and errors in setup.
Other than Django, Stack was our go to place to look for help on whatever problem we were stuck on and was definitely a huge help in this project.

Are other big source of information in learning how to use these all of these libraries and languages was the sources documentation.
When we needed to know about the internals of Django, a language quirk in Python, or how to display something in ArcGis, reading the documentation was usually our next step after checking StackOverflow.
Using the documentation was also important when we needed to go past surface level issues and do things that required harder knowledge.

One of our greatest resources when working on this project was each other.
While we had resources online that we could use, often times a member of the team would get stuck on something they weren't familiar with.
In these situations we were all very quick to ask for help and draw off of each other's knowledge and skills in order to solve a problem.
We complemented each other very well and did a good job of learning from each other throughout the project.
