% Your team weekly blog posts. These should be formatted nicely and clearly distinct from one another.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fall}

\subsubsection{Week 3 Update}
Accomplished last week:​

Met each other, we're all really cool dudes.
We then met with our client, David Lytle, and went over high-level project details to gain better understanding.
Created a rough draft of our project abstract.

Working on this Week:

Setting up touchpoint site and blog (yay).
​Finish final draft of abstract along with problem statement, solutions, etc.

Goals for next week:

Meet with client for more discussion and updates.
Work on whatever is assigned that week.


\subsubsection{Week 4 Update}
This week, we did not make progress on our project.
We reached out to schedule a meeting with our sponsor for next week so that we can put together requirements.
Our goal for next week is to have our requirements document finished.

\subsubsection{Week 5 Update}
This week we met with our TA to introduce ourselves and touch base.
We also met with our client Dave Lytle and talked about the requirements for the project.
This meeting gave us a more complete idea of what we were going to create and we then wrote up our requirements document.

\subsubsection{Week 6 Update}
This week we began revising our requirements document before receiving feedback from our TA in hopes to get a head-start on what sections we think he'll want us to supplement or rewrite.
We also had a team meeting for divvying up the portions on the technical review document.
We discussed the technologies we are reviewing for each solution so we could work on our sections on our own time.
Next week we will have it finished in time for turn in and start looking at the poster assignment.


\subsubsection{Week 7 Update}
​This week we did our rewrite on the requirement document, which mostly involved making our sharepoint gantt chart fit in a document.
We also wrote our Technical Review.
At this point we have a pretty good idea of what technologies we are going to use for each piece of our project.​​​ Next week we will work on our poster and our elevator pitch.

\subsubsection{Week 8 Update}
​This week, we killed it.
After we finished our technical review last week, we created the first draft of our poster.
It is very sparse at this point, since we haven't done any implementation.
However, it will be useful to get feedback on the poster now so that we can improve it for next term.
We also got an early start on our elevator pitch, which is going to be great.

\subsubsection{Week 9 Update}
After perfecting our elevator pitch to deliver in class we switched our sights to the design document project.
While we are still in the planning and structure phase of it, we will be begin writing the rough draft Monday next week.
With the holiday this week we won't be able to accomplish a whole lot, because we're each traveling a bit to visit family and won't be around.
Week 10 will be a major progress week for us.

\subsubsection{Week 10 Update}
Last week we began assigning portions and planning our design document.
We had already figured out our elevator speech and delivered that on Tuesday.
We had a good meeting with our TA Jon Dodge and made sure we were all on the same page for ending the term.
Our design document is now complete and ready to turn in (via hard-copy and email) and we are starting to plan / divvy up the progress report to turn in during finals week.

It's been a good term.
Our teamwork is strong, the project's goals are clear, and we're ready to dive head-first into some development.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Winter}

\subsubsection{Week 1 Update}
We neglected our project over break, so we spent this week doing a bit of catching up.
We worked on installing and configuring everything we need to get up and running.

We will need a web server, so we contacted our client about hosting one.
In the meantime, we will each host the website on our local machines.
The code will be kept in sync on GitHub.

We also worked on learning how to set up and use Django.
We have a Django project and app set up, and this is where we will do our backend development.

We had a bit of diffculty finding a good time for all of us to meet.
We want to spend a solid block of several hours working together each week.
This was tricky, but we have settled on Monday evenings at 6:30.
We worked together well, and spent our time productively.

For next week, we aim to have our web layout finished so there is something to look at.
We will also start working on manipulating the data into a relational database.

\subsubsection{Week 2 Update}
This week, we created our basic web layout.
We have a website, and it has a header and sections for each of the three main sections.
It uses bootstrap nicely, so that browser window size doesn't make our layout ugly.
The whole thing looks pretty slick.
Actually, it looks ugly as sin and has no content, but it's still impressive for a first start.

In the underlying code, each ​section (Map View, Statistics View, Filter View) is a separate view in a separate file.
We've assigned each team member to bring one view to alpha level functionality.
This will mean each view pulling in static data from the database.
Beta level will be allowing the filter view to actually control what is displayed in the map and graph views.

We worked well together this week.
We are meeting for a few hours a week to go over group stuff, and now have separate tasks to work on in the meantime.
We should be meeting with our TA later this week.
We still need to hear back from our client to get the cleaned up data, a hosting site, and an ArcGIS account though.

Next week, we will make  a script to import the raw data into our database.
This will be a big part of our alpha release.
Once we have data, we can actually display it and make it look pretty.
Hopefully, we can also start including that data in our views by next week as well.

\subsubsection{Week 3 Update - Jasper}
My task for this week was to finish alpha level functionality for the Filter View.
I finished this on time, but had to meet with Ty to figure out how to merge it into master.
I am yet a Git padawan.
Our meeting was more training on Degobah than productive work.
Stil, we got it merged, and now the filter view looks pretty.

The goal for this coming week is to start a script for importing the database from a CSV file.
We will work on this as a team, and we will need to meet with our sponsor first to clarify how the Database is to be set up.

\subsubsection{Week 4 Update - Jasper}
This week was a little slow.
I meant to make enhancements to the Filter View this week, but did not get around to it.
I did meet with the team to make our plan of attack for the midterm report.
We created a skeleton of the report.
We also started the database import process.
Our goal for next week is to have the website ready for alpha release.
This way, we can spend the following week focusing on writing it up and doing the video.​

\subsubsection{Week 3 Update - Ty}
This week the plan was to work with Jasper in settling merge conflicts from his branch containing the relevant ``filter-view" code, developing the script to import the bug data to MySQL​, and creating the models to map to the database.
Last week I was able to set up the webroot to be organized the way we want w/ all of our dependencies working and I developed the graph view with side scrolling capability and filler data.
Jasper and I have since settled the merge conflicts and merged his branch into master.
All that remains is Alec's code for the map view and we're near alpha-level release quality.
We decided to reach out to David about the data he supplied before importing it further, because we noticed some weird fields that may or may not be relevant and wanted to meet with him to figure out _exactly_ what we need.
Next week we will email him and/or meet w/ him if we can and clean up the main view whether or not we have the map view.

\subsubsection{Week 4 Update - Ty}
This week we were trying to get a better idea of how to handle the data and get all of our components into the repository.
I worked with Alec to get his database configured and his map view set up and he was also able to start thinking about ways to deploy our project.
We also met with David and his lab and went over more ideas and details on how to continue with the data.
We figured out some graphs that we might try to implement soon.
Basic ones for alpha release, but more complex ones for beta and after.
​Next week I want to work on making some improvements to the main interface and start working on the write up and video, since almost all the base components are in for the alpha.
We need to get the data in the database and render that data, but that shouldn't be too bad.

\subsubsection{Week 5 Update - Jasper}
This was a productive week.
Our team finished the database import script, so we are now ready to start supplying real data to the website.
I made the necessary additions and enhancements to the Filter View to get it ready for the alpha release.
These turned out to be relatively straightforward.
I also drafted my parts of the progress report.
I may need to add more content later.
Next week, our team will meet to finish the progress report and make the video.​ I'm pleased with our progress.

\subsubsection{Week 5 Update - Ty}
This week was very good for us.
All three of us met several times and created issues on github for tracking and setting goals for alpha and beta.
We established who needs to do what over the coming weekend to polish our alpha and to get crackin' on our report.
Alec and I met on Wednesday and managed to write an import script which parsed our clients excel spreadsheets and placed the data into our database correctly.
Now that all of us have working databases, providing info to our views shouldn't be a problem at all.
This next week we are all about working on the report, creating the video, and wrapping up our alpha.
We've divvied up the progress report so that everyone knows what they need to type up and each of us have one development task for alpha release.
Mine will be getting some better placeholder graphs, maybe even with some data in them. ​

\subsubsection{Week 6 Update - Jasper}
This week, I did my parts for the alpha release.
We got together as a team on Monday and recorded the video.
I gave an introduction to the project and talked about my contribution to the Filter View.
I also completed my writing sections for the report.
I wrote about the progress and work needed for the Filter View, as well as an intro and an overview of the graphs we will include for our beta release.
This was all relatively straightforward, since I had finished the necessary code last week.
Next week, we are working on getting data from the databse to actually display on the database.
My goal is to populate the Filter View with the actual data.

\subsubsection{Week 6 Update - Ty}
This week we were able to push our project into alpha and wrapped up those minor tasks.
We spent our meetings this week focused on writing our portions of the design document and filming our video.
We were able to shoot our video in one go after we each wrote an outline for ourselves on what we would say.
Our document was already split into portions from a previous meeting, so all we had to do was go back and fill out our sections.
Alec was kind enough to turn in the final product (document & video).
Next week we plan on working on getting our data dynamically into our views for all of our templates.
once the data has been initially rendered, we'll be able to finall start doing queries between views and hopefully stroll into beta. ​

\subsubsection{Week 7 Update - Ty}
This week we are working on getting data into our templates dynamically from the database.
Up until now it's been statically supplied.
We have all three views embedded and it's coming along nicely.
Next week we will focus on wrapping up all of our branches and getting them merged into master.
Then after that we will be tweaking the design in preparation for showing it to our customer next week.​

\subsubsection{Week 8 Update - Ty}
This week we showed our application to our customer and his team and it was very well received.
They liked it a lot in it's current state and it was really cool to get that kind of feedback.
Being able to see the product was really helpful for all of us to talk about goals moving forward and visualizing requests.
​Afterwards we went to the library and made some changes we talked about in the meeting.
we added all of our beta features to the github issue tracker in order to better keep ourselves in order.
We're gonna try to work on the site simultaneously with our report/video rework.

\subsubsection{Week 9 Update - Ty}
This week I was able to get the filtered data to create a fancy new chart based on what was selected in that view.
Thanks to Jasper, who got the filter object created after a successful post request, I was able to then piggyback on that process and set my graph labels and x-axis values to whatever is necessary to zoom in on that dataset.
I was really worried that this'd be the hardest thing to do, but now that we have one done we are going to totally be able to crush this and have beta looking good.
For the rest of this week I am going to be focusing on learning how to use LaTex and start getting some content into that paper.
I think next week​ our group is going to continue getting work done on the project along with cleaning up our poster and creating the video.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spring}

\subsubsection{Week 2 Update - Jasper}
This week, our team met to assign jobs for the 1.0 release.
Most of our tasks involved fixing bugs.
In fact, we powered through a bunch of bugs at our meeting.
I fixed ​the NULL and repeat entries that were showing up in the filter view, which makes it look much cleaner.
In fact, our website overall is looking much cleaner.
Hopefully, we'll be able to fix our last bugs soon and proceed to our stretch goals.
Exciting!

\subsubsection{Week 2 Update - Ty}
This week we got together and ironed out the rest of what was to be done for the 1.0 release.
We found about 8 minor issues with our beta release that could be smoothed over that covered small code refactors, more specific database queries, and some data massaging.
We found an interesting issue with how to go about handling NULL entries in the database, because while they're un-labeled, they were still a reading at some taxanomic level and we're not sure whether to count it once total, once each, or not at all.
This is definitely something to bring up to David or his team very soon to get ironed out. ​

\subsubsection{Week 3 Update - Ty}
This week we were able to meet with Richard, an associate of our primary client, and go over some of the data decisions covered in our posts from last week.
Without going into too much detail, he said that we were probably safe to disregard any NULL datapoints on the levels at which they occur.
This means tracking the taxa as long as it's identified in the graphs, but as soon as the level we're looking into has any undefined sub-levels we will ignore them from the plots.
Outside of the primary data issue, we demo'd our project for him and he was very happy with it.
During the demo he showed us how  they'd probably spend their time using it, so we found a couple more minor bugs that we'll address soon.
Other than that we will be wrapping up our poster and focusing on our documentation soon!

\subsubsection{Week 4 Update - Ty}
This week we made great progress towards being finished with our project.
Firstly, we were able to close all but 1 or 2 minor issues on github​.
The remaining issues are further testing/code clean-up along with a bit more visual functionality that Alec is gonna take care of regarding data points on the map.
Next we were able to get the cosine labs to open our server to IPs off-campus.
Finally, we got our poster ironed out with a couple iterations of review from Jon.
Next week we are going to be wrapping up our midterm report and video on Wednesday.
We reached out for a meeting with Dave Lytle and he said he could meet in a week or so, since he's been out travelling.
We're excited to show him how far we've come!

\subsubsection{Week 5 Update - Jasper}
This week, we got everything ready for the upcoming deadlines.
I am finished with all of my assigned issues on GitHub.
I finished my sections of the report, which had only minor edits to make.
I also made the necessary changes to my sections of the video, which were also minor.

I forgot my blog posts during the last several weeks, during which time I was mainly working on my issues on GitHub.
We also met with our sponsor's grad student during that time to show him the current state of our product.
He was really pleased with it.

Next week, I'll probably be focused on my thesis, but if I have some spare time, I might get a start on the final documentation, if the assignment for that is up by then.

\subsubsection{Week 5 Update - Ty}
This week was primarily focused around our documentation and presentation goals.
We revisted our final report from last term and cut out sections that need updating and those that we can re-use.
Our video is finished at the moment, leaving only our document.
I still have one issue on Github for labeling the graphs, but I should be able to get that done soon.
​Next week we will be meeting with our client and reconnecting after a long time due to his business trip.

\subsubsection{Week 6 Update - Ty}
This week we are fully finished with our project.
I was able to close out the last issue and Alec was able to set a meeting with our client.
We spent a majority of our time wrapping up the production report (mid-spring term report) and video.
That's all submitted and now we're just preparing for expo and documenting the code.
​This week we plan to meet with our client to touch base and show him the full product.
We've sent him all of our correspondence and a link to the live site, but it'll still be good to have a face to face meeting.
We're now in full expo preparation mode.

\subsubsection{Week 7 Update - Ty}
This week we finally closed all of our issues on github and met with our client for a pre-expo meeting.
Now that we're fully polished and feature complete, showing off the product to David was really fun and exciting.
He and his team are ecstatic about our product and want us to potentially want to scale it out later this year.
This next week is expo and we're spending this time preparing for that.
This means making sure we have our poster, we have nice clothing, etc. ​

\subsubsection{Week 8 Update - Ty}
Expo Expo Expo.
It was a long day of delivering the same shpeal to many people and standing in uncomfortable shoes, but it went really well.
We got a lot of good feedback on our project and were able to strike up potential continued development interest with many different groups.
I'm glad that it's done and that we're complete on the project.
This coming week we have lecture on Wednesday, which will be a big recap and Kevin's unveiling of our final write up for the term and project.
It will be a bitter-sweet process to have to write another, more comprehensive, paper and have to say goodbye to our project. ​​

\subsubsection{Week 9 Update - Ty}
This week our group met to divvy out responsibilities on the final paper/presentation.
We each have equal sections to write and will be filming our presentation this Wednesday.
Other than that there's no more development being done and we're focusing on ending the term well.

\subsubsection{Week 10 Update - Ty}
This was our last week for capstone as a whole.
We met once on Wednesday to film the remaining portions of our video and discuss the document.
Over the coming week we'll merge our individual branches for our paper and be completely finished!
It was a fun class and I'm glad I had the Jasper and Alex as teammates, Jon as a TA, and David's lab as a sponsor :) ​

\subsubsection{Week 10 Update - Jasper}
It's the end of Senior Capstone!
Last week, we got our final report set up and assigned tasks.
This week, we finished our final video presentation.
Now all that's left to do is finish up the final report and write group evaluations.
It's been a great year, and I'm really pleased with how Capstone has gone.
